---
title: "Final project - Airbnb Pricing in Amsterdam"
author: Lukas Cerno, Hederik de Vries & Casper Roex
date: "16 June 2016"
output: html_document
---

This report analyses a data set from Airbnb, an online broker for short-stay housing around the world, to detect the impact of housing attributes on per night prices. A subset was used of [xxx] properties in the centre of Amsterdam, with price per night divided by the maximum number of guests regressed on a number of explanatory variables. These variables include the number of bedrooms per guest, the quality of the host (as a function of rating and number of reviews), the level of privacy (shared room, private room, or entire apartment), and several amenities (airconditioning, free parking, WiFi, washing machine, and bath). We find that ….


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=TRUE, eval=FALSE, tidy=TRUE}
getwd()
setwd("../Final-project")
list.files()
rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
```

```{r echo=TRUE, eval=TRUE, tidy=TRUE}
ProjectData <- read.csv("Data/Airbnb_main.csv", sep=";", dec=",") # this contains only the matrix ProjectData
```

```{r}
ProjectData$priceperguest = ProjectData$price / ProjectData$accommodates
ProjectData$sharedroom = ifelse(ProjectData$room_type == "Shared room", 1 ,0)
ProjectData$private_room = ifelse(ProjectData$room_type == "Private room", 1 ,0)
ProjectData$bedroomsperguest = ProjectData$bedrooms / ProjectData$accommodates
ProjectData$realbed = ifelse(ProjectData$bed_type == "Real Bed" ,1 ,0)
```


```{r}
Subset_full <- subset(ProjectData, select = c("id","price","neighbourhood_cleansed","priceperguest","sharedroom","private_room","bedroomsperguest","realbed","review_scores_rating","Air.Conditioning","Free.Parking.on.Premises","Wireless.Internet","Washer","Hot.Tub","Pets.Allowed"))
Subset_full <- na.omit(Subset_full)
```

```{r}
Subset_num <- subset(ProjectData, select = c("price","priceperguest","sharedroom","private_room","bedroomsperguest","realbed","review_scores_rating","Air.Conditioning","Free.Parking.on.Premises","Wireless.Internet","Washer","Hot.Tub","Pets.Allowed"))
Subset_num <- na.omit(Subset_num)
```
## Business objective


## Including Plots


```{r echo=TRUE, eval=TRUE, tidy=TRUE}
hist(ProjectData[,"price"], 
     freq=TRUE,breaks=100, main="Histogram of Airbnb prices (in $)", include.lowest=TRUE)
```



```{r echo=FALSE, comment=NA, warning=FALSE, message=FALSE, results='asis'}
show_data = data.frame(cbind(colnames(Subset_num), round(cor(Subset_num),2)))
m1<-gvisTable(show_data,options=list(width=1920, height=min(400,27*(nrow(show_data)+1)),allowHTML=TRUE))
print(m1,'chart')

```

```{r echo=TRUE, eval=TRUE, tidy=TRUE}
#RegressionData <- ProjectData[,c("property_type","room_type","cancellation_policy","host_response_rate","host_acceptance_rate","host_listings_count","accommodates","bedrooms","neighbourhood_cleansed","price","security_deposit","minimum_nights","number_of_reviews","review_scores_rating","review_scores_accuracy","review_scores_cleanliness","review_scores_checkin","review_scores_communication","review_scores_location","review_scores_value")]
plot(Subset_num, pch=16, col="blue", main="Matrix Scatterplo")
```

```{r echo=TRUE, eval=TRUE, tidy=TRUE}
property_type = ProjectData[,"property_type"]
room_type = ProjectData[,"room_type"]
cancellation_policy = ProjectData[,"cancellation_policy"]
host_response_rate = ProjectData[,"host_response_rate"]
host_acceptance_rate = ProjectData[,"host_acceptance_rate"]
host_listings_count = ProjectData[,"host_listings_count"]
accommodates = ProjectData[,"accommodates"]
bedrooms = ProjectData[,"bedrooms"]
neighbourhood_cleansed = ProjectData[,"neighbourhood_cleansed"]
price = ProjectData[,"price"]
security_deposit = ProjectData[,"security_deposit"]
minimum_nights = ProjectData[,"minimum_nights"]
number_of_reviews = ProjectData[,"number_of_reviews"]
review_scores_rating = ProjectData[,"review_scores_rating"]
review_scores_accuracy = ProjectData[,"review_scores_accuracy"]
review_scores_cleanliness = ProjectData[,"review_scores_cleanliness"]
review_scores_checkin = ProjectData[,"review_scores_checkin"]
review_scores_communication = ProjectData[,"review_scores_communication"]
review_scores_location = ProjectData[,"review_scores_location"]
review_scores_value = ProjectData[,"review_scores_value"]
summary(lm(price ~ factor(property_type)+factor(room_type)+factor(cancellation_policy)+host_listings_count+accommodates+bedrooms+factor(neighbourhood_cleansed)+security_deposit+minimum_nights+number_of_reviews+review_scores_rating+review_scores_accuracy+review_scores_cleanliness+review_scores_checkin+review_scores_communication+review_scores_location))
```

```{r echo=TRUE, eval=TRUE, tidy=TRUE}

```



